### 2023-02-26 code/processing_code/3_cleaning_race_df.Rmd
eda

```{r}
black_df <- race_df %>% select(1:3, contains("Black"))

@@

hispanic_df <- race_df %>% select(1:3, contains("Hispanic"))

@@

white_df <- race_df %>% select(1:3, contains("White"))

@@

multiple_df <- race_df %>% select(1:3, contains("Multiple"))

>>>>

```{r}
black_df <- race_df %>% select(1:3, contains("Black"), 50:62)

@@

hispanic_df <- race_df %>% select(1:3, contains("Hispanic"), 50:62)

@@

white_df <- race_df %>% select(1:3, contains("White"), 50:62)

@@

multiple_df <- race_df %>% select(1:3, contains("Multiple"), 50:62)
